Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-12 treestats_paper.tex
Delete comment that is addressed in "Duality in practice" section

\krt{I have related concerns. What does it mean to look at a branch stat and a site state
    from an inferred tree sequence?  The input genotype data are informative about both 
    the inferred edges and their branch lengths.   So it seems to me that comparing the two types of stats is comparing
    non-independent quantities, and I am unclear how to interpret that? (I admit to not studying the GEVA paper closely
yet, nor the Speidel).  Presumably, the site stat is going to give you the right value (e.g., match whatever the
original paper reported for, say, pi), but the branch version of the stat could differ from this for perhaps a lot 
of reasons that all contribute to "edge estimation error"?  Not calling variants below a certain frequency,
preferentially calling variants you've seen in a previous study, or imputing in variants from other studies?
Overall, I have to squint at Fig S2 to see differences, and most of the issue seems to be near what I assume to be a
centromere?}

>>>>

\krt{
Overall, I have to squint at Fig S2 to see differences, and most of the issue seems to be near what I assume to be a
centromere?}
